Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.

>>>>

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards ubiquitous sensing and data capture~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, or miscellaneous networked devices. Many have worked to discover how privacy will be preserved in world of nearing omni-present sensors. Examples of such efforts include frameworks to design for privacy environments~\cite{bellotti1993design} and evaluating ubiquitous computing applications~\cite{scholtz2004toward}. There are also various models for understanding privacy with respect to ubiquitous computing, including a risk-based model~\cite{hong2004privacy} and a social-based model~\cite{jiang2002approximate}.
